Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Put the table inside the datalen figure.
Add concurrent graph to paper.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and \meek\ running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
Table~\ref{tab:datalen} summarizes the most common values.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{table}[ht]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[height=\linewidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:conconns}
\end{figure}

\subsection{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google user made
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1--10.

% David: I think this needs to be justified. Leaving Gmail open all day is a common use case,
% as is YouTube, as is finding +1 buttons and Google-source JavaScript on unrelated web sites.
% This is not unexpected
% because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

We measure the number of concurrent HTTPS connections during the automated browsing of Alexa
top 500 sites using three platforms: Tor Browser Bundle, Safari + Firefox extension, and Safari + Chrome extension.
Figure ~\ref{fig:conconns} shows the number over time. We can see that most of the time
the browser has one HTTPS connection to Google. Sometimes the browser may have more than one connection
due to background activities such as statistics reporting. In all cases the number of connections is always 
less than 5. We can conclude that the number of concurrent connections does not show distinct characteristics, as 
a small number of connections can be considered as a normal behavior.

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and \meek\ running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

@@

\subsection{Concurrent connections}

% Output of concurrent.R.
% [1] 2745
% [1] 2.610621
% [1] 1
% [1] 1.002148

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The LBL trace shows 2,745 unique clients and the meek trace only one.
The dark line is a smoothed average number of connections per client.
The meek count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the LBL trace is 2.61,
and in the meek trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how meek tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the LBL trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case if very heavily skewed to smaller numbers.
The average number of connections in the LBL trace is 2.61,
while that in the meek trace is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that a small number of concurrent connections is unremarkable.
